Prestige as a Driving Force in Cultural Transmission

### 2022-03-28 ms/PrestigeBias.tex
reformat as paper

\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}          
\usepackage{graphicx}
\usepackage{amsthm, amsmath, amssymb}
\usepackage[font=small]{caption, subcaption}
\usepackage{setspace}\onehalfspacing
\usepackage[loose,nice]{units}
\usepackage{array}
\usepackage[super]{nth}
\usepackage{graphicx}
\usepackage{float}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{mathtools}
\usepackage[displaymath, mathlines]{lineno}
\usepackage{natbib}
\usepackage[all]{nowidow}
\usepackage{wrapfig}
\usepackage{pdfpages}

@@

% math stuff
\DeclareMathOperator*{\E}{{\rm I\kern-.3em E}}
\let\vec\mathbf
\newenvironment{conditions}
  {\par\vspace{\abovedisplayskip}\noindent\begin{tabular}{>{$}l<{$} @{${}={}$} l}}
  {\end{tabular}\par\vspace{\belowdisplayskip}}

% title page stuff
\author{
	Saar Egozi
	\and
	Yoav Ram
}

\begin{document}

\begin{titlepage}
\centering

\vspace{4cm}

{\LARGE\bfseries Prestige as a Driving Force in Cultural Transmission}

\vspace{2cm}

{\large\bfseries Saar Egozi}

\vspace{1cm}

{\large supervised by Dr. Yoav Ram}

\vspace{2cm}

\vfill

{\large Efi Arazi School of Computer Science, Reichman University}

\vspace{1cm}

{\itshape \today}

{\large saartk@gmail.com}
\end{titlepage}

\renewcommand\linenumberfont{\normalfont\small\sffamily}
\linenumbers
\modulolinenumbers[2]
\setcounter{secnumdepth}{0}
\tableofcontents

\clearpage

\section{Abstract}
Copying role-models can be an efficient method of acquiring knowledge \citep{strategiesPaper}. \textbf{Here, we study the effects of prestige as a cultural transmission bias} in cultural-evolution model. A common bias when choosing a role-model to copy is \textit{success bias}, i.e copying whoever appears more successful \citep{evolution_of_cultural_evolution}. This bias depends on the performance of the role-model alone, without other factors. We propose an additional bias that may be prevalent in cultural transmission: \textit{Influence bias}, which is evaluated by the number of individuals that have already copied a specific role-model \citep{prestige_evolution}. We combine these biases together to a \textit{prestige bias} and analyze its effects on the evolutionary dynamics of the population using mathematical analysis and stochastic simulations. We find analytic approximations to our model, facilitating further mathematical analysis and reducing the computational complexity of the simulations. We validate these approximations using simulations, and demonstrate their robustness to model assumptions.
For a dichotomous cultural trait, we find  an approximation to the fixation probability and the fixation time of an invading advantageous cultural trait, in both a constant and changing environment, which resembles Kimura's classical formulas.
These approximations show that influence effectively reduces the population size. % TODO reduce or increase?
We also find that influence accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
Our model may provide a better description of how human cultural transmission, 
especially in the last years where social networks are very popular. % TODO to discuss this last sentence
Further work is needed to test if this model could predict various phenomena in human cultural evolution when extended with the effects of selection and innovation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Models and Methods}

@@

\subsection{Continuous trait}
We follow the model of \citet{evolutionBook}, assuming only oblique transmission of the indicator trait and omitting the indirect trait in order to reduce model complexity. 
We consider a population of $N$ individuals, described by a single indicator trait with a continuous value.
Each generation, $N$ naive individuals, or copiers, choose an individual from the previous generation, or role-models, from which they will copy their trait. Similar to a Wright–Fisher model, we assume non-overlapping generations such that the entire population is replaced in each generation.
The population at time $t$ can be described by $\vec{A}(t)=\big(A_{1}(t), \ldots, A_{N}(t)\big)$ where $A_{i}(t)$ is trait value of individual $i$ at time $t$. We assume the initial population is drawn from a standard normal distribution, $\vec{A}(0) \sim N(0,1)$ .
Cultural transmission is modeled by a function $F$ such that 
\begin{equation}\label{eq:transmission}
A_{i}(t+1) = F_i(\vec{A}(t)) \;.
\end{equation}

@@

\subsection{Dichotomous trait}
To allow for mathematical analysis of the model, we introduce a simplified version where the indicator trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$. 
All role-models with the same phenotype will contribute to the probability of that phenotype to be transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
Therefore, the probability of the $i$-th copier to copy phenotype $A$ is
% based on \cref{eq:copier_choose} is % TODO you refer an equation that did not yet appear!
\begin{equation}\label{eq:binary-model}
P_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + X\alpha'\beta(\hat{A})} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} % TODO should it be G_{i,A} rather than P_i,A ?
\end{equation}
where $X$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model.
% TODO what is alpha' ?
Initially, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. The rest of the details follow the continuous trait model.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Approximations}
Our model is defined by two nested stochastic processes. Change over multiple generations is described by the phenotype distribution at each generation, $\{\vec{A}(t)\}_t$. The transition from one generation to the next is described by the number of copiers each role-model has after $i$ copiers have chosen a role-model, $\{\vec{K}_i\}_{i=1}^N$.
We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$. However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}. Thus, we sought to find an equivalent stochastic process that has the same joint distribution as $\vec{K}_{N}$. 
We found two approximations such processes, summarized here and explained in detail below:
\begin{enumerate}
\item 
The number of copiers of a specific role-model at each step, $K_{i,j}$, follows the {\em generalized binomial distribution}~\citep{GBD} and therefore,
\begin{enumerate}\item the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers, that is,
$\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$).
\item the expected number of copiers of each role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if $\alpha$ is uniform for all role-models ($\alpha=\alpha_k$ for $k=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated indicator value. 
\end{enumerate}
\item The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$). 
Therefore, the number of copiers of all role-models, $\vec{K}_i = (K_{i,1}, \ldots, K_{i,N})$, follows a Dirichlet-Multinomial distribution,
$\vec{K}_i \sim \mathit{DM}\big(N, \vec{G}_1\big)$, where $\vec{G}_1 = (G_{1,1}, \ldots, G_{1,N})$ is the prestige vector of all role-models in the "eyes" of the first copier.
Note that here $G_{i,j}$ is only a function of the indicator values $A_j$ and the weights $\alpha_j$, as the estimation error is uniform. % TODO correct? anything else need to be assumed?
\end{enumerate}

\subsection{Generalized Binomial Distribution Approximation}
The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is parameterized by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials ($\theta=0$ gives the standard binomial distribution).

\paragraph{Proposition.} The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A_j+e))$ if $e_i=e$ for all role-models $i=1, \ldots, N$.

\paragraph{Proof.} We denote $Q_j(k,i)=P(K_{i,j} = k \mid K_{i-1,j})$ as the probability that exactly $k$ out of $i$ copiers choose role-model $j$ given $K_{i-1,j}$ our of $i-1$ copiers chose role-model $j$. 
Using conditional probability and \cref{eq:recurrence},
\begin{equation}\label{recursive}
Q_j(k,i) = P_j(S_{i,j}=1 | k-1,i-1) \cdot Q_j(k-1,i-1) + P_j(S_{i,j} =0 | k,i-1) \cdot Q_j(k,i-1),
\end{equation}
where $S_{i,j} =1 $ when the $i$-th copier chooses role-model $j$.
\Cref{recursive} is equivalent to eq.~(2.1) by \citet{GBD}, which completes the proof.
%$Q_j(k,N)$ is the probability that $k$ out of $N$ copiers choose role-model $j$ at the end of the process, which by our previous notation is $k=K_{N,j}$. % TODO do you need this sentence?

\paragraph{Corollary 1.} $\E[K_{N,j}] = N \cdot G_{1,j}$.
\paragraph{Proof.} \citet[eq.~(2.3)]{GBD} show that 
$\E[k] = N \cdot Q_j(1,1)$ (modified from their notation).
$Q_j(1,1)$ is the initial probability to choose role-model $j$, before any role-model choices are made.
$Q_j(1,1) = G_{1,j}$ by definition, which completes the proof.

\paragraph{Corollary 2: } $\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
\paragraph{Proof.} The initial prestige of role-model $j$ based on \cref{eq:prestige} is
\begin{equation}\label{eq:initial_prob}
G_{1,j} = \frac{\alpha_j\cdot\beta(A_j+e)}{\sum\limits_{m=1}^{N} \alpha_m\cdot\beta(A_m+e)} \;.
\end{equation}
The denominator of \cref{eq:initial_prob} can also be formulated as:
\begin{equation}\label{eq:denominator}
 \sum\limits_{m=1}^{N}\alpha_m\beta(A_m+e) = N \cdot \overline{\alpha \cdot \beta(A+e)} \;,
\end{equation}
where $\overline{\alpha\beta(A+e)}$ is the mean value of $\alpha_m\cdot\beta(A_m+e)$ for all $m$.
Using \cref{eq:denominator} we get, % TODO something is missing here? how did you get E[KNj] to relate to the previous two equations?
\begin{equation}
\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) \bigg/ \overline{\alpha \cdot \beta(A+e)} \;,
\end{equation}
completing the proof.

@@

\subsection{Dirichlet-Multinomial Distribution Approximation}
\paragraph{Reminder: \textit{Pólya urn model}}  is a stochastic process that is defined as such: 
The process consists of $N$ draws from an urn with an initial amount of colored balls of $M$ colors. When a ball is drawn, it is then placed back in the urn together with an additional new ball of the same colour.\\
Let $\vec{U_i} = \{u_{i,1},u_{i,2},...,u_{i,M}\}$  where $u_{i,j}$ is the number of balls of the $j$-th color in the urn after $i$ draws.
Let $S_{i,j}=1$ when drawing a $j$ colored ball on the $i$-th draw, and $0$ otherwise. The probability that $S_{i,j}=1$ given $\vec{U_{i-1}}$ is:
\begin{equation}\label{polya}
\begin{split}
P(S_{i,j} = 1 | \vec{U_{i-1}}) & = \frac{u_{i-1,j}}{\sum\limits_{m=1}^{M} u_{i-1,m}} = \frac{o_j + w_{i-1,j}}{\sum\limits_{m=1}^{M} o_m + w_{i-1,m}}\\
 & = \frac{o_j + w_{i-1,j}}{i-1 + \sum\limits_{m=1}^{M} o_m}
\end{split}
\end{equation}
where $o_j$ is the initial number of balls of the colour $j$ in the urn, and $w_{i,j}$ is the number of new balls that were added to the urn after $i$ draws of the color $j$.

\paragraph{Proposition:} process $\big\{\vec{K}_i\big\}_{i=1}^N$ is equivalent to a \textit{Pólya urn model} when $e=e_i=e_j$ and $\alpha=\alpha_j=\alpha_i$ for all $i,j \in N$.
\paragraph{Proof:} 
We denote $\alpha'$ as the odds ratio between the weights of the indicator and the influence ($\alpha'=\frac{\alpha}{1-\alpha}$). 
Using \cref{eq:prestige} we get:
\begin{equation}\label{eq:copier_choose}
\begin{split}
G_{i,j} & = \frac{\alpha\cdot \beta(A'_j) + (1-\alpha) \cdot K_{i-1,j}}{W_i} \cdot \frac{1-\alpha}{1-\alpha} \\
&= \frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N} \alpha'\beta(A'_m) + K_{i-1,m}}\\
& =\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{i-1 + \sum\limits_{m=1}^{N} \alpha'\beta(A'_m)}
\end{split}
\end{equation}
We see that \cref{polya} and \cref{eq:copier_choose} are equivalent when setting $M=N$, $o_j = \alpha'\beta(A'_j)$, $w_{i,j} = K_{i,j}$, completing the proof.

\paragraph{Corollary 1:}
In their paper, \citet[section 2]{dirichlet} prove that the proportion of different colored balls in a \textit{Pólya urn model} will converge to the Dirichlet distribution as the number of draws approaches infinity, based on \textit{Martingale Convergence Theorem} \citep{martingaleBook}.
We therefore have an approximation for the relative "weight" or the proportion each role-model has when evaluated as a role-model. Drawing from a Multinomial distribution where the parameters are the modified weights gained from the Dirichlet distribution is viable for selecting the role-model for the next generation.
We can therefore sample from a Dirichlet-Multinomial distribution to approximate how many copiers each of the role-models will have:
$\vec{K_i} \sim DM(N,\vec{G_1})$.

@@

\subsection{Numeric comparisons}
We're interesting in studying the difference between the real binary model as we defined in \cref{eq:binary-model}, and the Dirichlet-Multinomial approximation. Specifically, we're interesting in the fixation probability of the favored trait ($\hat{A}$) and its time to fixation.

@@

\subsection{Fixation probability and time - binary model}
\paragraph{Kimura's approximation:}
After establishing a case in the favor of our DM approximation, we wanted to use it to examine the behavior of the population. Specifically, we wanted to analyze the influence of the indicator weight ($\alpha$) on the fixation probability and time to fixation of the favored phenotype in a binary model.
For simplicity, we don't include mutation rate in the binary model approximations.
Following \citet{durret}, we used our DM approximation of the model to find the effective population size. From \cref{eq:binary-model} we can derive that the process of inheritance in our binary model is DM distributed with a parameters vector of size two: $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$.

\paragraph{Proposition:} $1-\beta(A)$ is equivalent to the selection coefficient $s$ in a classic Wright-Fisher model in the diffusion equations meant to approximate the fixation probability and time of the advantageous trait.

\paragraph{Proof:} Let $x$ be the frequency of type $\hat{A}$ in the population with $N$ individuals. Let $X$ be the number of individuals of type $\hat{A}$ so $x=X/N$. $X'$ is the number of individuals with $\hat{A}$ in the next generation and $x'$ their frequency.
By definition $\beta(\hat{A})=1$, and for simplicity we'll denote $\beta(A)=\beta$ ($\beta<1$).

@@

By definition, $x$ is constant, so $E[x] = x$. We continue to calculate $E[x'-x]$:
\begin{equation}\label{eq:expec_freq}
E[x'-x] = E[x'] - E[x] = x(1-x)(1-\beta) + o(1-\beta)
\end{equation}
where when substituting $1-\beta$ with $s$, we get the same result as \citet{durret} which is the desired result.

\paragraph{Proposition:} $Ne=\alpha N + (1-\alpha)$, where $Ne$ is the effective population size of our binary model.

\paragraph{Proof:} The variance of a DM distribution is:
\begin{equation}
V(X') = N\frac{\alpha_1}{\alpha_1+\alpha_2}(1-\frac{\alpha_1}{\alpha_1+\alpha_2})
(\frac{N + \alpha_1+\alpha_2}{1+\alpha_1+\alpha_2})
\end{equation}
And again, we want to use frequencies so:
\begin{equation}
V(\frac{X'}{N}) = \frac{1}{N^2}V(x')
\end{equation}

@@

\subsection{Changing environment}
After finding good estimations for our model in a constant environment, when the favorable trait is always $\hat{A}$, we want to find an estimation for our model in a changing environment.

>>>>

\documentclass[12pt]{extarticle}
\usepackage{geometry}
\geometry{
a4paper,
total={170mm,257mm},
left=20mm,
top=20mm,
headheight=12pt
}

%\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amsthm, amsmath, amssymb}
\usepackage[font=small]{caption, subcaption}
\usepackage{setspace}\onehalfspacing
\usepackage[loose,nice]{units}
\usepackage{array}
\usepackage[super]{nth}
\usepackage{graphicx}
\usepackage{float}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{mathtools}
\usepackage[round,colon,authoryear]{natbib}
\usepackage[all]{nowidow}
\usepackage{wrapfig}
\usepackage{pdfpages}
\usepackage{authblk}

@@

% math stuff
\DeclareMathOperator*{\E}{{\rm I\kern-.3em E}}
\newcommand*{\tr}{^\intercal}
\let\vec\mathbf
\newcommand{\matrx}[1]{{\left[ \stackrel{}{#1}\right]}}
\newcommand{\diag}[1]{\mbox{diag}\matrx{#1}}
\newcommand{\goesto}{\rightarrow}
\newcommand{\dspfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2} }
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}
\newtheorem{result}{Result}
\renewcommand\qedsymbol{} % no square at end of proof
\newcommand{\cl}{\mathbf{L}}
\newcommand{\cj}{\mathbf{J}}
\newcommand{\ci}{I}

% title page stuff
\title{Prestige as a Driving Force in Cultural Transmission}

\author[1]{Saar Egozi}
\author[2,3,*]{Yoav Ram}
\affil[1]{School of Computer Science, Reichman University, Herzliya, Israel}
\affil[2]{School of Zoology, Faculty of Life Sciences, Tel Aviv University, Tel Aviv, Israel}
\affil[3]{Sagol School of Neuroscience, Tel Aviv University, Tel Aviv, Israel}
\affil[*]{Corresponding author: yoav@yoavram.com}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
Copying role-models can be an efficient method of acquiring knowledge. Here, we study the effects of prestige as a cultural transmission bias in cultural-evolution model. A common bias when choosing a role-model to copy is success bias, i.e copying whoever appears more successful. This bias depends on the performance of the role-model alone, without other factors. We propose an additional bias that may be prevalent in cultural transmission: influence bias, which is evaluated by the number of individuals that have already copied a specific role-model . We combine these biases together to a prestige bias and analyze its effects on the evolutionary dynamics of the population using mathematical analysis and stochastic simulations. We find analytic approximations to our model, facilitating further mathematical analysis and reducing the computational complexity of the simulations. We validate these approximations using simulations, and demonstrate their robustness to model assumptions.
For a dichotomous cultural trait, we find  an approximation to the fixation probability and the fixation time of an invading advantageous cultural trait, in both a constant and changing environment, which resembles Kimura's classical formulas.
These approximations show that influence effectively reduces the population size. % TODO reduce or increase?
We also find that influence accelerates the evolutionary dynamics, as can be expected in a \textit{rich-getting-richer} process.
Our model may provide a better description of how human cultural transmission, 
especially in the last years where social networks are very popular. % TODO to discuss this last sentence
Further work is needed to test if this model could predict various phenomena in human cultural evolution when extended with the effects of selection and innovation.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Models and Methods}

@@

\subsection*{Continuous trait}
We follow the model of \citet{evolutionBook}, assuming only oblique transmission of the indicator trait and omitting the indirect trait in order to reduce model complexity. 
We consider a population of $N$ individuals, described by a single indicator trait with a continuous value.
Each generation, $N$ naive individuals, or copiers, choose an individual from the previous generation, or role-models, from which they will copy their trait. Similar to a Wright–Fisher model, we assume non-overlapping generations such that the entire population is replaced in each generation.
The population at time $t$ can be described by $\vec{A}(t)=\big(A_{1}(t), \ldots, A_{N}(t)\big)$ where $A_{i}(t)$ is trait value of individual $i$ at time $t$. We assume the initial population is drawn from a standard normal distribution, $\vec{A}(0) \sim N(0,1)$ .
Cultural transmission is modeled by a function $F$ such that 
\begin{equation}\label{eq:transmission}
A_{i}(t+1) = F_i(\vec{A}(t)) \;.
\end{equation}

@@

\subsection*{Dichotomous trait}
To allow for mathematical analysis of the model, we introduce a simplified version where the indicator trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$. 
All role-models with the same phenotype will contribute to the probability of that phenotype to be transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
Therefore, the probability of the $i$-th copier to copy phenotype $A$ is
% based on \cref{eq:copier_choose} is % TODO you refer an equation that did not yet appear!
\begin{equation}\label{eq:binary-model}
P_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + X\alpha'\beta(\hat{A})} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} % TODO should it be G_{i,A} rather than P_i,A ?
\end{equation}
where $X$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model.
% TODO what is alpha' ?
Initially, we assume the population has a single individual with phenotype $\hat{A}$ and $N-1$ individuals with phenotype $A$. The rest of the details follow the continuous trait model.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
\subsection*{Approximations}
Our model is defined by two nested stochastic processes. Change over multiple generations is described by the phenotype distribution at each generation, $\{\vec{A}(t)\}_t$. The transition from one generation to the next is described by the number of copiers each role-model has after $i$ copiers have chosen a role-model, $\{\vec{K}_i\}_{i=1}^N$.
We emphasize that the models are nested: $\vec{A}(t+1)$ can be computed from $\vec{A}(t)$ by evaluating $\vec{K}_{N}$. However, the former requires iterating over \cref{eq:recurrence,eq:recPrestige}. Thus, we sought to find an equivalent stochastic process that has the same joint distribution as $\vec{K}_{N}$. 
We found two approximations such processes, summarized here and explained in detail below:
\begin{enumerate}
\item 
The number of copiers of a specific role-model at each step, $K_{i,j}$, follows the {\em generalized binomial distribution}~\citep{GBD} and therefore,
\begin{enumerate}\item the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers, that is,
$\E[K_{N,j}] = N \cdot G_{1,j}$ if trait estimation error is uniform for all copiers ($e=e_i$ for $i=1, \ldots, N$).
\item the expected number of copiers of each role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models, that is, $\E[K_{N,j}] = \beta(A_j+e) / \overline{\beta}$ if $\alpha$ is uniform for all role-models ($\alpha=\alpha_k$ for $k=1,\ldots,N$), where $\overline{\beta}=1/N \sum_{j=1}^{N}{\beta(A_j+e)}$ is the population mean estimated indicator value. 
\end{enumerate}
\item The role-model choice process, $\{\vec{K}_{i}\}_{i=1}^{N}$, is equivalent to a {\em P\'{o}lya urn} model if trait estimation error is uniform for all copiers ($e=e_i$ for all $i=1, \ldots, N$). 
Therefore, the number of copiers of all role-models, $\vec{K}_i = (K_{i,1}, \ldots, K_{i,N})$, follows a Dirichlet-Multinomial distribution,
$\vec{K}_i \sim \mathit{DM}\big(N, \vec{G}_1\big)$, where $\vec{G}_1 = (G_{1,1}, \ldots, G_{1,N})$ is the prestige vector of all role-models in the "eyes" of the first copier.
Note that here $G_{i,j}$ is only a function of the indicator values $A_j$ and the weights $\alpha_j$, as the estimation error is uniform. % TODO correct? anything else need to be assumed?
\end{enumerate}

\subsection*{Generalized Binomial Distribution}
The generalized binomial distribution (GBD) emerges from a series of dependent Bernoulli trials (in contrast to the standard binomial distribution in which trials are independent) and is parameterized by $GBD(n, p, \theta)$ where $n$ is the number of trials, $p$ is the probability of success of the first trial, and $\theta$ is the correlation between trials ($\theta=0$ gives the standard binomial distribution).

\begin{result}[GBD approximation]
The number of copiers of role-model $j$ after $i$ copiers have chosen a role-model follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A_j+e))$ if $e_i=e$ for all role-models $i=1, \ldots, N$. 
\end{result}

\begin{proof}
We denote $Q_j(k,i)=P(K_{i,j} = k \mid K_{i-1,j})$ as the probability that exactly $k$ out of $i$ copiers choose role-model $j$ given $K_{i-1,j}$ our of $i-1$ copiers chose role-model $j$. 
Using conditional probability and \cref{eq:recurrence},
\begin{equation}\label{recursive}
Q_j(k,i) = P_j(S_{i,j}=1 | k-1,i-1) \cdot Q_j(k-1,i-1) + P_j(S_{i,j} =0 | k,i-1) \cdot Q_j(k,i-1),
\end{equation}
where $S_{i,j} =1 $ when the $i$-th copier chooses role-model $j$.
\Cref{recursive} is equivalent to eq.~(2.1) by \citet{GBD}, which completes the proof.
%$Q_j(k,N)$ is the probability that $k$ out of $N$ copiers choose role-model $j$ at the end of the process, which by our previous notation is $k=K_{N,j}$. % TODO do you need this sentence?
\end{proof}

\begin{corollary}
$\E[K_{N,j}] = N \cdot G_{1,j}$.
\end{corollary}

\begin{proof}
\citet[eq.~(2.3)]{GBD} show that 
$\E[k] = N \cdot Q_j(1,1)$ (modified from their notation).
$Q_j(1,1)$ is the initial probability to choose role-model $j$, before any role-model choices are made.
$Q_j(1,1) = G_{1,j}$ by definition, which completes the proof.
\end{proof}

\begin{corollary}
$\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) / \overline{\alpha \cdot \beta(A+e)}$, where the averaging in the denominator is over the role-models index, $j$.
\end{corollary}

\begin{proof}
The initial prestige of role-model $j$ based on \cref{eq:prestige} is
\begin{equation}\label{eq:initial_prob}
G_{1,j} = \frac{\alpha_j\cdot\beta(A_j+e)}{\sum\limits_{m=1}^{N} \alpha_m\cdot\beta(A_m+e)} \;.
\end{equation}
The denominator of \cref{eq:initial_prob} can also be formulated as:
\begin{equation}\label{eq:denominator}
 \sum\limits_{m=1}^{N}\alpha_m\beta(A_m+e) = N \cdot \overline{\alpha \cdot \beta(A+e)} \;,
\end{equation}
where $\overline{\alpha\beta(A+e)}$ is the mean value of $\alpha_m\cdot\beta(A_m+e)$ for all $m$.
Using \cref{eq:denominator} we get, % TODO something is missing here? how did you get E[KNj] to relate to the previous two equations?
\begin{equation}
\E[K_{Nj}] = \alpha_j \cdot \beta(A_j+e) \bigg/ \overline{\alpha \cdot \beta(A+e)} \;,
\end{equation}
completing the proof.
\end{proof}

@@

\subsection*{Dirichlet-Multinomial Distribution}

\begin{remark}
\textit{Pólya urn model}  is a stochastic process that is defined as such: 
The process consists of $N$ draws from an urn with an initial amount of colored balls of $M$ colors. When a ball is drawn, it is then placed back in the urn together with an additional new ball of the same colour.\\
Let $\vec{U_i} = \{u_{i,1},u_{i,2},...,u_{i,M}\}$  where $u_{i,j}$ is the number of balls of the $j$-th color in the urn after $i$ draws.
Let $S_{i,j}=1$ when drawing a $j$ colored ball on the $i$-th draw, and $0$ otherwise. The probability that $S_{i,j}=1$ given $\vec{U_{i-1}}$ is:
\begin{equation}\label{polya}
\begin{split}
P(S_{i,j} = 1 | \vec{U_{i-1}}) & = \frac{u_{i-1,j}}{\sum\limits_{m=1}^{M} u_{i-1,m}} = \frac{o_j + w_{i-1,j}}{\sum\limits_{m=1}^{M} o_m + w_{i-1,m}}\\
 & = \frac{o_j + w_{i-1,j}}{i-1 + \sum\limits_{m=1}^{M} o_m}
\end{split}
\end{equation}
where $o_j$ is the initial number of balls of the colour $j$ in the urn, and $w_{i,j}$ is the number of new balls that were added to the urn after $i$ draws of the color $j$.
\end{remark}

\begin{result}[Pólya urn model]
$\big\{\vec{K}_i\big\}_{i=1}^N$ is equivalent to a \textit{Pólya urn model} when $e=e_i=e_j$ and $\alpha=\alpha_j=\alpha_i$ for all $i,j \in N$.
\end{result}

\begin{proof} 
We denote $\alpha'$ as the odds ratio between the weights of the indicator and the influence ($\alpha'=\frac{\alpha}{1-\alpha}$). 
Using \cref{eq:prestige} we get:
\begin{equation}\label{eq:copier_choose}
\begin{split}
G_{i,j} & = \frac{\alpha\cdot \beta(A'_j) + (1-\alpha) \cdot K_{i-1,j}}{W_i} \cdot \frac{1-\alpha}{1-\alpha} \\
&= \frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N} \alpha'\beta(A'_m) + K_{i-1,m}}\\
& =\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{i-1 + \sum\limits_{m=1}^{N} \alpha'\beta(A'_m)}
\end{split}
\end{equation}
We see that \cref{polya} and \cref{eq:copier_choose} are equivalent when setting $M=N$, $o_j = \alpha'\beta(A'_j)$, $w_{i,j} = K_{i,j}$, completing the proof.
\end{proof}

\begin{remark}
In their paper, \citet[section 2]{dirichlet} prove that the proportion of different colored balls in a \textit{Pólya urn model} will converge to the Dirichlet distribution as the number of draws approaches infinity, based on \textit{Martingale Convergence Theorem} \citep{martingaleBook}.
We therefore have an approximation for the relative "weight" or the proportion each role-model has when evaluated as a role-model. Drawing from a Multinomial distribution where the parameters are the modified weights gained from the Dirichlet distribution is viable for selecting the role-model for the next generation.
We can therefore sample from a Dirichlet-Multinomial distribution to approximate how many copiers each of the role-models will have:
$\vec{K_i} \sim DM(N,\vec{G_1})$.
\end{remark}

@@

\subsection*{Numeric comparisons}
We're interesting in studying the difference between the real binary model as we defined in \cref{eq:binary-model}, and the Dirichlet-Multinomial approximation. Specifically, we're interesting in the fixation probability of the favored trait ($\hat{A}$) and its time to fixation.

@@

\subsection*{Fixation probability and time - binary model}
\paragraph{Kimura's approximation:}
After establishing a case in the favor of our DM approximation, we wanted to use it to examine the behavior of the population. Specifically, we wanted to analyze the influence of the indicator weight ($\alpha$) on the fixation probability and time to fixation of the favored phenotype in a binary model.
For simplicity, we don't include mutation rate in the binary model approximations.
Following \citet{durret}, we used our DM approximation of the model to find the effective population size. From \cref{eq:binary-model} we can derive that the process of inheritance in our binary model is DM distributed with a parameters vector of size two: $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$.

\begin{result}[Effective selection coefficient]
$1-\beta(A)$ is equivalent to the selection coefficient $s$ in a classic Wright-Fisher model in the diffusion equations meant to approximate the fixation probability and time of the advantageous trait.
\end{result}

\begin{proof}
Let $x$ be the frequency of type $\hat{A}$ in the population with $N$ individuals. Let $X$ be the number of individuals of type $\hat{A}$ so $x=X/N$. $X'$ is the number of individuals with $\hat{A}$ in the next generation and $x'$ their frequency.
By definition $\beta(\hat{A})=1$, and for simplicity we'll denote $\beta(A)=\beta$ ($\beta<1$).

@@

By definition, $x$ is constant, so $E[x] = x$. We continue to calculate $E[x'-x]$:
\begin{equation}\label{eq:expec_freq}
E[x'-x] = E[x'] - E[x] = x(1-x)(1-\beta) + o(1-\beta)
\end{equation}
where when substituting $1-\beta$ with $s$, we get the same result as \citet{durret} which is the desired result.
\end{proof}

\begin{result}[Effective population size]
$N_e=\alpha N + (1-\alpha)$, where $Ne$ is the effective population size of our binary model.
\end{result}

\begin{proof}
The variance of a DM distribution is:
\begin{equation}
V(X') = N\frac{\alpha_1}{\alpha_1+\alpha_2}(1-\frac{\alpha_1}{\alpha_1+\alpha_2})
(\frac{N + \alpha_1+\alpha_2}{1+\alpha_1+\alpha_2})
\end{equation}
And again, we want to use frequencies so:
\begin{equation}
V(\frac{X'}{N}) = \frac{1}{N^2}V(x')
\end{equation}

@@

\subsection*{Changing environment}
After finding good estimations for our model in a constant environment, when the favorable trait is always $\hat{A}$, we want to find an estimation for our model in a changing environment.
